Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-05-25 draft/paper1_jenny.tex
New ellipticity and color gradient plot

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        Alexie Leauthaud,$^{2,1}$
        Jenny E. Greene,$^{4}$
        Kevin Bundy,$^{3,1}$
        Yen-Ting Lin,$^{5}$
        \newauthor
        Masayuki Tanaka,$^{6}$
        Rachel Mandelbaum,$^{7}$
        Satoshi Miyazaki,$^{5,8}$
        Yutaka Komiyama,$^{5,8}$
        HSC collaboration 
        \\
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
              Tokyo 181--8588, Japan\\
        $^{6}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{7}$McWilliams Center for Cosmology, Department of Physics, 
              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
        $^{8}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
              Tokyo, 181--8588, Japan
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}
      \centering 
      \includegraphics[width=\columnwidth]{fig/redbcg_discussion_2}
      \caption{
          \song{Update caption.}
          Radial variations in ellipticity and optical colors for massive galaxies. 
          The format of this figure is similar to the right hand side of 
          Fig~\ref{fig:prof_1}. 
          Top panels show the ellipticity profile, middle panels show $g-r$, and lower 
          panels show $g-i$. 
          We compare our results with those from \citet{Tal2011} based on stacking 
          large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
          (solid blue line on top panel). 
          We also compare with the results from a stacking analysis of nearby massive 
          galaxies with high concentration index ($C>2.6$) in 
          \citet[][blue dash lines on the top and middle panels]{DSouza2014}. 
          Finally, we also compare with the average $g-r$ and $g-i$ color profiles 
          from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
          lines on the middle and bottom panels]{LaBarbera2010}.
          }
      \label{fig:ell_color}
  \end{figure}
%% ------------------------------------------------------------------------------------ %%

>>>>

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        Alexie Leauthaud,$^{2,1}$
        Jenny E. Greene,$^{4}$
        Kevin Bundy,$^{3,1}$
        \newauthor
        Yen-Ting Lin,$^{5}$
        Masayuki Tanaka,$^{5}$
        Rachel Mandelbaum,$^{7}$
        Satoshi Miyazaki,$^{5,8}$
        \newauthor
        Yutaka Komiyama,$^{5,8}$
        HSC collaboration 
        \\
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
              Tokyo 181--8588, Japan\\
        $^{6}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{7}$McWilliams Center for Cosmology, Department of Physics, 
              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
        $^{8}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
              Tokyo, 181--8588, Japan
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_ell_color.pdf}
      \caption{
          \song{Update caption.}
          Radial variations in ellipticity and optical colors for massive galaxies. 
          The format of this figure is similar to the right hand side of 
          Fig~\ref{fig:prof_1}. 
          Top panels show the ellipticity profile, middle panels show $g-r$, and lower 
          panels show $g-i$. 
          We compare our results with those from \citet{Tal2011} based on stacking 
          large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
          (solid blue line on top panel). 
          We also compare with the results from a stacking analysis of nearby massive 
          galaxies with high concentration index ($C>2.6$) in 
          \citet[][blue dash lines on the top and middle panels]{DSouza2014}. 
          Finally, we also compare with the average $g-r$ and $g-i$ color profiles 
          from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
          lines on the middle and bottom panels]{LaBarbera2010}.
          }
      \label{fig:ell_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%
